---
title: "statsForAim3"
output: html_document
date: "2022-12-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load required R packages 
library(readxl)
library(tidyverse)
library(rstatix)
library(ggpubr)


# Loading the slip MTU, MG, and AT excursion lengths
setwd("C:/GitHub/Perception-Project/Dan/USPercep Analysis/Analysis/")
Slipsdata<- read_excel("DataFormatForStats_US2(DJL).xlsx", sheet = "AvgSlips") %>%
	as_tibble()
Slipsdata %>%



# Putting data in long format for the multiple comparisons 
Slipsdata.long <- Slipsdata %>%
  pivot_longer(-Perceived, names_to = "variables", values_to = "value")
Slipsdata.long %>% sample_n(6)




# Running stats for MTU, MG, and AT excursion Slips
statSlips.test <- Slipsdata.long %>%
  group_by(variables) %>%
  wilcox_test(value ~ Perceived, alternative = "less") %>%
  adjust_pvalue(method = "holm") %>%
  add_significance()
statSlips.test

```{r statSlips.test}
print.data.frame(head(statSlips.test))
```


# Loading the Trip Peak PID MTU, MG, and AT excursion lengths
setwd("C:/GitHub/Perception-Project/Dan/USPercep Analysis/Analysis/")
pSlipsdata <- read_excel("DataFormatForStats_US2(DJL).xlsx", sheet = "PeakSlips") %>%
	as_tibble()
pSlipsdata %>%



# Putting data in long format for the multiple comparisons 
pSlipsdata.long <- pSlipsdata %>%
  pivot_longer(-Perceived, names_to = "variables", values_to = "value")
pSlipsdata.long %>% sample_n(6)




# Running stats for MTU, MG, and AT excursion trips
statpSlips.test <- pSlipsdata.long %>%
  group_by(variables) %>%
  wilcox_test(value ~ Perceived, alternative = "less") %>%
  adjust_pvalue(method = "holm") %>%
  add_significance()
statpSlips.test

```{r statpSlips.test}
print.data.frame(head(statpSlips.test))
```

# Loading the Trip Peak PID MTU, MG, and AT excursion lengths
setwd("C:/GitHub/Perception-Project/Dan/USPercep Analysis/Analysis/")
tSlipsdata <- read_excel("DataFormatForStats_US2(DJL).xlsx", sheet = "TimeSlips") %>%
	as_tibble()
tSlipsdata %>%



# Putting data in long format for the multiple comparisons 
tSlipsdata.long <- tSlipsdata %>%
  pivot_longer(-Perceived, names_to = "variables", values_to = "value")
tSlipsdata.long %>% sample_n(6)




# Running stats for MTU, MG, and AT excursion trips
stattSlips.test <- tSlipsdata.long %>%
  group_by(variables) %>%
  wilcox_test(value ~ Perceived, alternative = "less") %>%
  adjust_pvalue(method = "holm") %>%
  add_significance()
stattSlips.test

```{r stattSlips.test}
print.data.frame(head(stattSlips.test))
```

# Loading the Trip average PID MTU, MG, and AT excursion lengths
setwd("C:/GitHub/Perception-Project/Dan/USPercep Analysis/Analysis/")
Tripsdata <- read_excel("DataFormatForStats_US2(DJL).xlsx", sheet = "AvgTrips") %>%
	as_tibble()
Tripsdata %>%



# Putting data in long format for the multiple comparisons 
Tripsdata.long <- Tripsdata %>%
  pivot_longer(-Perceived, names_to = "variables", values_to = "value")
Tripsdata.long %>% sample_n(6)




# Running stats for MTU, MG, and AT excursion Slips
statTrips.test <- Tripsdata.long %>%
  group_by(variables) %>%
  wilcox_test(value ~ Perceived, alternative = "less") %>%
  adjust_pvalue(method = "holm") %>%
  add_significance()
statTrips.test

```{r statTrips.test}
print.data.frame(head(statTrips.test))
```



# Loading the Trip Peak PID MTU, MG, and AT excursion lengths
setwd("C:/GitHub/Perception-Project/Dan/USPercep Analysis/Analysis/")
pTripsdata <- read_excel("DataFormatForStats_US2(DJL).xlsx", sheet = "PeakTrips") %>%
	as_tibble()
pTripsdata %>%



# Putting data in long format for the multiple comparisons 
pTripsdata.long <- pTripsdata %>%
  pivot_longer(-Perceived, names_to = "variables", values_to = "value")
pTripsdata.long %>% sample_n(6)




# Running stats for MTU, MG, and AT excursion trips
statpTrips.test <- pTripsdata.long %>%
  group_by(variables) %>%
  wilcox_test(value ~ Perceived, alternative = "less") %>%
  adjust_pvalue(method = "holm") %>%
  add_significance()
statpTrips.test

```{r statpTrips.test}
print.data.frame(head(statpTrips.test))
```

# Loading the Trip Peak PID MTU, MG, and AT excursion lengths
setwd("C:/GitHub/Perception-Project/Dan/USPercep Analysis/Analysis/")
tTripsdata <- read_excel("DataFormatForStats_US2(DJL).xlsx", sheet = "TimeTrips") %>%
	as_tibble()
tTripsdata %>%



# Putting data in long format for the multiple comparisons 
tTripsdata.long <- tTripsdata %>%
  pivot_longer(-Perceived, names_to = "variables", values_to = "value")
tTripsdata.long %>% sample_n(6)




# Running stats for MTU, MG, and AT excursion trips
stattTrips.test <- tTripsdata.long %>%
  group_by(variables) %>%
  wilcox_test(value ~ Perceived, alternative = "less") %>%
  adjust_pvalue(method = "holm") %>%
  add_significance()
stattTrips.test

```{r stattTrips.test}
print.data.frame(head(stattTrips.test))
```