---
title: "statsForAim2"
output:
  pdf_document: default
  html_document: default
date: "2022-12-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load required R packages 
library(readxl)
library(tidyverse)
library(rstatix)
library(ggpubr)

# Prepare the data and inspect a random sample of the data
setwd("C:/GitHub/Perception-Project/Dan/Data Processing and Analysis/WholeVsLocal/")
Wdata<- read_excel("DataFormatForR_WholeVLocal.xlsx", sheet = "Whole Avg ES Full GC") %>%
	as_tibble()
Wdata %>%


# Pulling out sections of WBAM, COM
WBAMdata <- Wdata %>%
  select(1:3,13)
WBAMdata %>%

CoMData <- Wdata %>%
  select(4:13)
CoMData %>%


# Putting data in long format for the multiple comparisons 
WBAMdata.long <- WBAMdata %>%
  pivot_longer(-Perceived, names_to = "variables", values_to = "value")
WBAMdata.long %>% sample_n(6)


CoMData.long <- CoMData %>%
  pivot_longer(-Perceived, names_to = "variables", values_to = "value")
CoMData.long %>% sample_n(6)


# Running stats for WBAM
statWBAM.test <- WBAMdata.long %>%
  group_by(variables) %>%
  wilcox_test(value ~ Perceived, alternative = "less") %>%
  adjust_pvalue(method = "holm") %>%
  add_significance()
statWBAM.test



```{r statWBAM.test}
print.data.frame(head(statWBAM.test))
```

# Running stats for WBAM
statCoM.test <- CoMData.long %>%
  group_by(variables) %>%
  wilcox_test(value ~ Perceived, alternative = "less") %>%
  adjust_pvalue(method = "holm") %>%
  add_significance()
statCoM.test


```{r statCoM.test}
print.data.frame(statCoM.test)
```




# Loading the local sensory data for stats
setwd("C:/GitHub/Perception-Project/Dan/Data Processing and Analysis/WholeVsLocal/")
Ldata<- read_excel("DataFormatForR_WholeVLocal.xlsx", sheet = "Local Avg ES Full GC") %>%
	as_tibble()
Ldata %>%



# Putting data in long format for the multiple comparisons 
Localdata.long <- Ldata %>%
  pivot_longer(-Perceived, names_to = "variables", values_to = "value")
Localdata.long %>% sample_n(6)




# Running stats for Local
statLocal.test <- Localdata.long %>%
  group_by(variables) %>%
  wilcox_test(value ~ Perceived, alternative = "less") %>%
  adjust_pvalue(method = "holm") %>%
  add_significance()
statLocal.test


```{r statLocal.test}
print.data.frame(statLocal.test)
```
